---
params: 
  title: ""
  publication_date: ""
  doi: ""
output: 
  html_document:
    anchor_sections: false
    theme: null
    highlight: null
    mathjax: null
    css: ["style.css", "https://fonts.googleapis.com/css?family=Source+Sans+Pro:400,700&display=swap"]
    self_contained: true
title: "`r params$title`"
---

```{r general-setup, include=FALSE}
## This file contains the ENGLISH version of the data story

# Set general chunk options
knitr::opts_chunk$set(
  echo = FALSE, fig.showtext = TRUE, fig.retina = 3,
  fig.align = "center", warning = FALSE, message = FALSE
)

# Install snf.datastory package if not available, otherwise load it
if (!require("snf.datastory")) {
  if (!require("devtools")) {
    install.packages("devtools")
    library(devtools)
  }
  install_github("snsf-data/snf.datastory")
  library(snf.datastory)
}

# Load packages
library(tidyverse)
library(lubridate)
library(scales)
library(conflicted)
library(jsonlite)
library(here)
library(glue)
library(ggiraph)

# Conflict preferences
conflict_prefer("filter", "dplyr")
conflict_prefer("get_datastory_theme", "snf.datastory")
conflict_prefer("get_datastory_scheme", "snf.datastory")

# Increase showtext package font resolution
showtext_opts(dpi = 320)

# Set the locale for date formatting (Windows)
Sys.setlocale("LC_TIME", "English")

# Create function to print number with local language-specific format
print_num <- function(x) snf.datastory::print_num(x, lang = "en")

# Knitr hook for local formatting of printed numbers
knitr::knit_hooks$set(
  inline <- function(x) {
    if (!is.numeric(x)) {
      x
    } else {
      print_num(x)
    }
  }
)
```

```{r print-header-infos, results='asis'}
# Add publication date to header
cat(format(as_datetime(params$publication_date), "%d.%m.%Y"))

# Register the Google font (same as Data Portal, is not loaded twice)
cat(paste0(
  "<link href='https://fonts.googleapis.com/css?family=",
  "Source+Sans+Pro:400,700&display=swap' rel='stylesheet'>"
))
```

```{r story-specific-setup, include=FALSE}
# Set story-specific variables etc. here
# Load the funding volume 1952-2021
yearly_data_1952_2021 <- read_csv(here("data", "yearly_data_1952_2021.csv"))

# Load the yearly research area shares 1952-2021
yearly_shares_1952_2021 <- 
  read_csv(here("data", "yearly_shares_1952_2021.csv")) %>% 
  mutate(research_area = fct_relevel(research_area, c("SSH", "MINT", "LS", 
                                                      "Interdisziplinär")))

# Load the yearly gender shares 1991-2021
yearly_gender_shares_1991_2021 <- 
  read_csv(here("data", "yearly_gender_shares_1991_2021.csv"))
```

**The SNSF has been awarding grants to research projects across all scientific disciplines since 1952. How has the amount of funding evolved over time?**

In the first few years of its existence, the SNSF contributed a few million francs each funding cycle to researchers in Switzerland. After ten years, in 1962, the funding pool amounted to CHF 23 million, which is equivalent to just under CHF 100 million today. Thereafter, the amount of funding increased to CHF 150 million by 1979 (about CHF 300 million today). During the first half of the 1980s, funding stagnated, then rose to around CHF 360 million by 1996 (around CHF 400 million today). After stagnating again up to the early 2000s, funding increased more or less steadily, reaching an all-time high of CHF `r print_num(1152)` million in 2018.

Note that awards made during the four-year planning periods, and generally for some funding schemes, are not linear over the years but are subject to fluctuations. This also largely explains the decline in funding since 2018. All these figures include funding for the <a href="https://www.snf.ch/en/FJBJ8XGQ1tjG8J8w/funding/programmes/national-centres-of-competence-in-research-nccr" target="_blank">National Centres of Competence in Research (NCCRs)</a>.

<div class="hide-mobile hide-tablet widemedia">

<div class="plot-box">
<div class="plot-title">Total funds awarded (in CHF millions)</div>

```{r funding-volume-plot-desktop, out.width="100%", fig.height=4}
# Function to draw the funding volume plot
draw_plot_funding_volume <- function() {
  # Create ggplot plot
  ggplot_plot <- yearly_data_1952_2021 %>% 
    ggplot(aes(x = year, 
               y = amount / 1000000, 
               tooltip = paste0(year, ": ", if_else(year <= 2001, 
                                                    "approx.", ""), 
                                " ", round(amount / 1000000), 
                                " million awarded"))) + 
    geom_col_interactive(fill = get_datastory_scheme()[1]) + 
    # scale_y_continuous(breaks = seq(0, 1300, 100), limits = c(0, 500)) +
    # coord_flip() + 
    labs(
      # title = "Entwicklung des Fördervolumens", 
      # subtitle = "Ohne Horizon Europe Übergangsmassnahmen", 
      x = NULL, y = NULL) + 
    get_datastory_theme()
  
  # Create ggiraph object
  girafe(ggobj = ggplot_plot, 
         height_svg = 4, 
         options = list(
           opts_toolbar(saveaspng = FALSE),
           opts_hover(css = "fill:#F08262;stroke:#F08262;"),
           opts_tooltip(
             css = get_ggiraph_tooltip_css(),
             opacity = 0.8,
             delay_mouseover = 0,
             delay_mouseout = 0
           )
         ))
}

# Draw the plot for desktop
draw_plot_funding_volume()
```

<div class="caption">
Detailed figures can be found in the individual annual reports. The chart shows nominal figures, not adjusted for inflation. Yearly allocations for 2002–2021 are based on the following data (in order of availability): call decision year, grant application decision year, year of submission.
</div>
</div>
</div>

<div class="hide-desktop">

<div class="plot-box">
<div class="plot-title">Total funds awarded (in CHF millions)</div>

```{r funding-volume-plot-mobile, out.width="100%", fig.height=4}
# Draw the plot for mobile
draw_plot_funding_volume()
```

<div class="caption">
Detailed figures can be found in the individual annual reports. The chart shows nominal figures, not adjusted for inflation. Yearly allocations for 2002–2021 are based on the following data (in order of availability): call decision year, grant application decision year, year of submission.
</div>
</div>
</div>

### Distribution stable across research areas since 1975

Until 1975, mathematics, natural and engineering sciences (MINT) dominated with up to 73% of annual funding, driven by nuclear and energy research. Worth noting is the decline in the social sciences and humanities (SSH) from about one-third in the founding period to less than 10% in the 1960s.

<div class="plot-box">

<div class="plot-title">Percentage of grants awarded by research area</div>

```{r example-plot-2, out.width="100%", fig.height=10}
# Create ggplot plot
ggplot_plot <- yearly_shares_1952_2021 %>% 
  # Translate and order the research areas
  mutate(
    research_area = case_when(
      research_area == "SSH" ~ "SSH", 
      research_area == "MINT" ~ "MINT", 
      research_area == "LS" ~ "LS", 
      research_area == "Interdisziplinär" ~ "Interdisciplinary", 
      TRUE ~ "UNKNOWN"
    ), 
    # Longer label for the plot tooltip
    research_area_long = case_when(
      research_area == "SSH" ~ 
        "social sciences and humanities (SSH)", 
      research_area == "MINT" ~ 
        "mathematics, natural and engineering sciences (MINT)", 
      research_area == "LS" ~ 
        "life sciences (LS)", 
      research_area == "Interdisziplinär" ~ 
        "interdisciplinary research", 
      TRUE ~ "UNKNOWN"
    ), 
    research_area = fct_relevel(research_area, c("SSH", "MINT", "LS", 
                                               "Interdisciplinary"))) %>% 
  # mutate(year = as_factor(year)) %>% 
  ggplot(aes(x = year, 
             y = perc, fill = fct_rev(research_area), 
             tooltip = paste0(year, ": ", round(perc), 
                              "% of funds allocated for ", 
                              research_area_long))) + 
  # Hack: Add a geom_col under the interactive one, only to be able to provide
  # correct looking legend items (round although bar chart), 
  # geom_col_interactive does not take the argument 'key_glyph'
  geom_col(width = 0.1, size = 0.1,
           # Draw point instead of square symbol
           key_glyph = draw_key_dotplot) +
  # Add ggiraph column, don't show it in legend as we're using points (and not 
  # squares) according to the style guide there (see hack before)
  geom_col_interactive(show.legend = FALSE) + 
  geom_text(aes(label = paste0(round(perc), "%")), 
            position = position_stack(vjust = 0.6), color = "white", 
            size = 2.5, family = "Source Sans Pro") +
  scale_x_reverse(breaks = c(seq(1952, 2012, 10), 2021)) +
  scale_y_continuous(labels = percent_format(accuracy = 1, scale = 1)) + 
  coord_flip() + 
  labs(
    # title = "Granted amount per budget year and research area", 
       # subtitle = "Horizon Europe Transitional Measures excluded", 
       x = NULL, y = "Share of granted amount") + 
  scale_fill_manual(values = rev(get_datastory_scheme(n_col = 4)), 
                    guide = guide_legend(reverse = TRUE)) + 
  get_datastory_theme()

# Create ggiraph object
girafe(ggobj = ggplot_plot, 
       height_svg = 10, 
       options = list(
         opts_toolbar(saveaspng = FALSE),
         opts_hover(css = "fill:#F08262;stroke:white;"),
         opts_tooltip(
           css = get_ggiraph_tooltip_css(),
           opacity = 0.8,
           delay_mouseover = 0,
           delay_mouseout = 0
         )
       ))
```

<div class="caption">
Detailed figures can be found in the individual annual reports. Yearly allocations for 2002–2021 are based on the following data (in order of availability): call decision year, grant application decision year, year of submission. The figures exclude NCCRs and transitional measures for Horizon 2020. The grants for 2002–2021 were assigned to the research areas based on the primary discipline.
</div>

Since 1975, the figures show an almost constant distribution between mathematics, natural and engineering sciences (approx. 40%), life sciences (LS, approx. 40%) and social sciences and humanities (20%). Although the number of grants awarded to SSH is similar to other research areas, the amount of funds is only about half as large due to the lower average grant. In 2016, the SNSF explicitly awarded grants to interdisciplinary research for the first time, which reduced the share of the MINT disciplines and life sciences to some extent. 

### More funding for female researchers

The proportion of funded female researchers increased from 10% in 1991 to more than one-third in 2021. This evolution is constant over time, with no individual years standing out.

<div class="plot-box">
<div class="plot-title">Percentage of grants approved by gender</div>

```{r gender-grantee, out.width="100%", fig.height=6.5}
# Create ggplot plot
ggplot_plot <- yearly_gender_shares_1991_2021 %>%  
  mutate(ResponsibleApplicantGender = 
           if_else(ResponsibleApplicantGender == "f", 
                   "Woman as corresponding applicant", 
                   "Man as corresponding applicant"), 
         ResponsibleApplicantGender = fct_relevel(
           ResponsibleApplicantGender, 
           c("Woman as corresponding applicant", 
             "Man as corresponding applicant"))) %>% 
  ggplot(aes(x = year, y = freq, fill = fct_rev(ResponsibleApplicantGender), 
             tooltip = paste0(year, "; ", ResponsibleApplicantGender, ": ", 
                              round(freq * 100), "%"))) + 
  # Hack: Add a geom_col under the interactive one, only to be able to provide
  # correct looking legend items (round although bar chart), 
  # geom_col_interactive does not take the argument 'key_glyph'
  geom_col(width = 0.1, size = 0.1,
           # Draw point instead of square symbol
           key_glyph = draw_key_dotplot) +
  # Add ggiraph column, don't show it in legend as we're using points (and not 
  # squares) according to the style guide there (see hack before)
  geom_col_interactive(show.legend = FALSE) + 
  labs(x = NULL, y = NULL) + 
  geom_text(aes(label = paste0(round(freq * 100), "%")), 
            position = position_stack(vjust = 0.6), color = "white", 
            size = 2.5, family = "Source Sans Pro") +
  scale_x_reverse(breaks = seq(1991, 2021, 2)) +
  scale_y_continuous(labels = percent_format(accuracy = 1)) + 
  scale_fill_manual(values = rev(get_datastory_scheme(n_col = 2)), 
                    guide = guide_legend(reverse = TRUE)) + 
  get_datastory_theme() + 
  coord_flip()

# Create ggiraph object
girafe(ggobj = ggplot_plot, 
       height_svg = 6.5, 
       options = list(
         opts_toolbar(saveaspng = FALSE),
         opts_hover(css = "fill:#F08262;stroke:white;"),
         opts_tooltip(
           css = get_ggiraph_tooltip_css(),
           opacity = 0.8,
           delay_mouseover = 0,
           delay_mouseout = 0
         )
       ))
```

<div class="caption">
For the yearly allocations for 1991–2021, the following data were used (in order of availability): call decision year, grant application decision year, year of submission. The figures exclude NCCRs and transitional measures for Horizon 2020. The grants for 2002–2021 were assigned to the research areas based on the primary discipline.
</div>

<div class="hide-mobile hide-tablet">
<strong>Useful links</strong>
<p>
  <a href="https://www.snf.ch/en/otHGxR771A58l7BM/news/snsf-investing-in-researchers-and-their-ideas-for-70-years" target="_blank" class="button-blue">News about the 70th anniversary</a>
  <a href="https://www.snf.ch/de/SmhGfltIQkzzCxJc/seite/ueberuns/portraet/geschichte" target="_blank" class="button">History of the SNSF</a>
</p>
</div>
<div class="hide-desktop">
<strong>Useful links</strong>
<p>
  <a href="https://www.snf.ch/en/otHGxR771A58l7BM/news/snsf-investing-in-researchers-and-their-ideas-for-70-years" target="_blank" class="button-blue">News about the 70th anniversary</a><br/><br/>
  <a href="https://www.snf.ch/de/SmhGfltIQkzzCxJc/seite/ueberuns/portraet/geschichte" target="_blank" class="button">History of the SNSF</a>
</p>
</div>

Data, text and code of this data story are <a href="https://github.com/snsf-data/70_years_snsf" target="_blank">available on Github</a> and <a href="https://doi.org/10.46446/datastory.70-years-snsf-from-a-few-million-to-a-billion" target="_blank">archived on Zenodo</a>.<br>DOI: 10.46446/datastory.70-years-snsf-from-a-few-million-to-a-billion

```{r prevent-internal-snsf-packages, include=FALSE}
# Internal SNSF packages must not be used in data stories, as their
# pre-processing functions are internal and the corporate design differs from
# the data portal.
if (any(c("snfverse", "snf.preprocessing", "snf.plot") %in% 
        loadedNamespaces())) {
  stop(glue(
    "You must not use internal SNSF packages in data stories.",
    " Please resort to snf.datastory."
  ))
}
```